---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
date: "2024-04-19"
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

#start of thesis:

```{r, echo=FALSE, message=FALSE}
#install.packages("nortest")
#install.packages("estimatr")
library(readr)
library(broom)
library(data.table)
library(car)
library(MASS)
library(olsrr)
library(lmtest)
library(nortest)
library(sandwich)
library(estimatr)
```

```{r, echo=FALSE, message=FALSE}
UR <- read_csv("unique reviews.csv")
setDT(UR)
```
Creating the variables Age and Helpfulness_percentage_positive. Also use scaling in order to standardize our metric independent variables

```{r}

# Standardize the independent variables
UR$Age <- as.numeric(max(UR$Date_of_Review) - UR$Date_of_Review)# subtraction by min to numeric
UR$Verification <- scale(UR$Verification)
UR$Amount_of_positive_attributes <- scale(UR$Amount_of_positive_attributes)
UR$Amount_of_negative_attributes <- scale(UR$Amount_of_negative_attributes)
UR$Amount_of_neutral_attributes <- scale(UR$Amount_of_neutral_attributes)
UR$Rating_Extremeness <- scale(UR$Rating_Extremeness)
UR$Age <- scale(UR$Age)
UR$Helpfulness_percentage_positive <- UR$Helpfulness_Positive / (UR$Helpfulness_Positive+UR$Helpfulness_Negative)

UR$Helpfulness_percentage_positive[is.na(UR$Helpfulness_percentage_positive)] <- 0


```


```{r}
View(UR)
summary(UR)
```


```{r}
UR_lm1 <- lm(Helpfulness ~ Verification +Amount_of_positive_attributes +Amount_of_negative_attributes+Amount_of_neutral_attributes +Rating_Extremeness +Verification*Age, UR);

UR_lm2 <- lm(Helpfulness_percentage_positive ~ Verification +Amount_of_positive_attributes +Amount_of_negative_attributes+Amount_of_neutral_attributes +Rating_Extremeness +Verification*Age, UR);

summary(UR_lm1)
summary(UR_lm2)

```



```{r}
UR_lm1_robust <- lm_robust(Helpfulness ~ Verification +Amount_of_positive_attributes +Amount_of_negative_attributes+Amount_of_neutral_attributes +Rating_Extremeness +Verification*Age, UR);

UR_lm2_robust <-lm_robust(Helpfulness_percentage_positive ~ Verification +Amount_of_positive_attributes+Amount_of_negative_attributes+Amount_of_neutral_attributes +Rating_Extremeness +Verification*Age, UR)

summary(UR_lm1_robust)
summary(UR_lm2_robust)

```



Assumptions

# Homoscedasticity

model 1
```{r}

bptest(UR_lm1)
# Plot residuals vs. fitted values also linearity check
plot(UR_lm1$fitted.values, UR_lm1$residuals,
     xlab = "Fitted Values",
     ylab = "Residuals",
     main = "Residuals vs. Fitted Values",
     pch = 16,      # Set point character to solid circle
     col = "blue",  # Set point color to blue
     cex = 0.8)     # Set point size
```

model 2
```{r}

bptest(UR_lm2)
# Plot residuals vs. fitted values also linearity check
plot(UR_lm2$fitted.values, UR_lm2$residuals,
     xlab = "Fitted Values",
     ylab = "Residuals",
     main = "Residuals vs. Fitted Values",
     pch = 16,      # Set point character to solid circle
     col = "blue",  # Set point color to blue
     cex = 0.8)     # Set point size
```

model 1 robust
```{r}

bptest(UR_lm1_robust)
# Plot residuals vs. fitted values also linearity check
plot(UR_lm1_robust$fitted.values, UR_lm1_robust$residuals,
     xlab = "Fitted Values",
     ylab = "Residuals",
     main = "Residuals vs. Fitted Values",
     pch = 16,      # Set point character to solid circle
     col = "blue",  # Set point color to blue
     cex = 0.8)     # Set point size
```

model 2 robust
```{r}

bptest(UR_lm2_robust)
# Plot residuals vs. fitted values also linearity check
plot(UR_lm2_robust$fitted.values, UR_lm2_robust$residuals,
     xlab = "Fitted Values",
     ylab = "Residuals",
     main = "Residuals vs. Fitted Values",
     pch = 16,      # Set point character to solid circle
     col = "blue",  # Set point color to blue
     cex = 0.8)     # Set point size
```


# Multicollinearity: if vif is below 10 for interaction or even 5 then we are good.

model 1
```{r}
vif(UR_lm1)
```

model 2
```{r}
vif(UR_lm2)
```



checking normality

model 1
```{r}
residuals<- residuals(UR_lm1)
ks.test(residuals, "pnorm")
ad.test(residuals(UR_lm1))
```

```{r}
hist(residuals(UR_lm1),main = "Histogram of Residuals", breaks=30)
```

```{r}
qqnorm(residuals(UR_lm1))#distribution of my model residuals
qqline(residuals(UR_lm1))#theoretic normal distr
```

model 2
```{r}
residuals<- residuals(UR_lm2)
ks.test(residuals, "pnorm")
ad.test(residuals(UR_lm2))
```

```{r}
hist(residuals(UR_lm2),main = "Histogram of Residuals", breaks=30)
```

```{r}
qqnorm(residuals(UR_lm2))#distribution of my model residuals
qqline(residuals(UR_lm2))#theoretic normal distr
```





Total Graphs used for interpretation

```{r}
ols_plot_diagnostics(UR_lm1)

```

```{r}
ols_plot_diagnostics(UR_lm2)

```

